---
title: "paindraw and paindrawr"
subtitle: "Software for capturing, vizualising and analyzing pain drawings"
author: "Steen Flammild Harsted and Søren O'Neill"
date: today
format:
  revealjs:
    theme: simple
    slide-number: true
    toc: false
    transition: slide
    incremental: false
    preview-links: auto
    css: custom.css
    code-fold: false
    embed-resources: true
    scrollable: true
execute: 
  warning: false
  message: false
  echo: true
editor: 
  markdown: 
    wrap: 72
---

```{r}
#| label: "Libraries and setup"
#| include: false
#| echo: false
#| code-fold: false

# USE THIS CODE in TERMINAL TO RENDER
# quarto preview /home/steen/projects/paindrawr/presentation/2026_09_15_KB.qmd --no-browser --no-watch-inputs

library(tidyverse)
library(here)
library(patchwork)
library(colorspace)
library(glue)
library(gt)
library(gtsummary)
library(devtools)
library(paindrawr)

theme_set(theme_classic(base_size = 14))
theme_gtsummary_compact()

# Load background images
bg_palmar <- here("inst/extdata/lower_arm_palmar.png")
bg_mird <- here("inst/extdata/mird_body_background.png")
bg_zealand <- here("inst/extdata/zealand.png")
```


```{r}
#| label: "load data"
#| include: false
#| echo: false
#| code-fold: false

# Get the Data 
# Get standard data
base_data <- read_csv(here("presentation", "2026_09_15_data.csv")) 

# Keep only relevant columns
base_data <- base_data |>
  select(
    record_id = "Record ID", 
    tool = "Please choose one of the two items", 
    distance = "Please choose a distance" , 
    geography = "How well do you know the geography of east Denmark?" 
  )


json_files <- list.files(
  here("presentation/2026_09_15_drawings/"),
  pattern = "json$",
  recursive = TRUE
)

paindraw_data <- tibble(
  pdr_data = pdr_import_json(here(
    "presentation/2026_09_15_drawings/",
    json_files
  ))
)

paindraw_data <- paindraw_data |> 
  mutate(
    id = pdr_get_info(pdr_data)
  )



## Id is nested in the drawing id string
paindraw_data <- paindraw_data |>
  mutate(
    record_id = str_extract(id, "R[0-9]+F") |>
      str_remove("^R") |>
      str_remove("F$") |>
      as.double()
  )

# Because we have multible drawings pr id we go wide before joining
### First extract image type
paindraw_data_wide <- paindraw_data |>
  mutate(
    view = str_extract(id, "F-.+-") |>
      str_remove("^F-") |>
      str_remove("-E.+$") |>
      str_remove("^background_image_")
  ) |>
  select(-id) |>
  pivot_wider(
    names_from = view,
    values_from = pdr_data
  )

my_data <- base_data |>
  left_join(paindraw_data_wide)


### START HERE
my_data

```


## The data {.smaller}

```{r}
#| label: "Show data"
#| echo: false
my_data 
```



# Imaginary hand pain

## Single drawing

```{r}
#| output-location: column-fragment
my_data |> 
  filter(record_id == 6) |> 
  pdr_plot_drawing(
    paindrawr_data = palmar
    )
```


## Single drawing

```{r}
#| output-location: column-fragment
my_data |> 
  filter(record_id == 6) |> 
  pdr_plot_drawing(
    paindrawr_data = palmar, 
    background_image = bg_palmar
    )
```

## 4x random drawings
```{r}
my_data |> 
  slice_sample(n = 4) |> 
  pdr_plot_drawing(
    paindrawr_data = palmar, 
    background_image = bg_palmar
    )
```


# Visual analysis of imaginary handpain

## Heatmpap

```{r}
my_data |> 
  pdr_plot_heatmap(
    paindrawr_data = "palmar", 
    background_image = bg_palmar)
```


## Heatmpap

### Hammer vs Apple
```{r}
my_data |> 
  pdr_plot_heatmap(
    paindrawr_data = "palmar", 
    variables = "tool",
    background_image = bg_palmar)
```

## Heatmpap

### 1m vs 1cm
```{r}
my_data |> 
  pdr_plot_heatmap(
    paindrawr_data = "palmar", 
    variables = "distance",
    background_image = bg_palmar)
```


## Heatmpap

### tool vs distance
```{r}
my_data |> 
  pdr_plot_heatmap(
    paindrawr_data = "palmar", 
    variables = c("tool", "distance"),
    background_image = bg_palmar)
```


# Quantitative analysis of imaginary handpain

## Add an rgba render {.smaller}
```{r}
my_data <- my_data |> 
  mutate(
    palmar = pdr_add_rgba(palmar))

my_data
```

## Get summary statistics {.smaller}

```{r}
my_data <- my_data |> 
  mutate(
    palmar_area = pdr_summarize_alpha_area(palmar), 
    palmar_intensity = pdr_summarize_alpha_intensity(palmar)
  )

my_data

```


## Summarize across groups {.smaller}

```{r}
my_data |> 
  group_by(tool, distance) |> 
  summarise(
    palmar_area_mean = mean(palmar_area, na.rm = TRUE), 
    palmar_area_sd  = sd(palmar_area, na.rm = TRUE)
  )
```


## Summarize across groups

```{r}
my_data |> 
  ggplot(aes(x = tool, y = palmar_area, fill = distance))+
  geom_boxplot(alpha = 0.5) 
```



