---
title: "Introduction to PaindrawR"
author: "S. O'Neill & S. Harsted"
format: 
  revealjs:
    code-fold: true
    code-summary: "Show the code"
    echo: true
    embed-resources: true
editor: source
---

```{r}
#| echo: false
library(tidyverse)
library(here)
library(paindrawr)
```

## Diving right in ...  {.hscroll .scrollable}

Pain drawings are stored as a _list-column_ in a data frame (a _tibble_)

```{r}
pdr_example_data[1:3,] |> dplyr::select(-pain)
```

## A single pain drawing

### from the pdr_data list-column

```{r}
pdr_example_data[1,]$pdr_data 
```

## Looking at a plot of the same data

```{r}
pdr_example_data[1,] |> pdr_plot_drawing()
```

## Re-introduced the canvas

```{r}
pdr_example_data[1,] |> 
  pdr_plot_drawing(background_image = pdr_example_file("mird_body_background.png"))
```

## A detour..

Another data set:

```{r}
pdr_example_anatomy
```

## Filtering and imploding drawings

```{r}
#| echo: true

pdr_example_anatomy |>
  filter(str_detect(id, "(Mid_back_bottom)|(Back.+(lowerback|buttock))")) |>
  pdr_implode() |> 
  mutate(pdr_data = pdr_polygonize(pdr_data)) |>
  pdr_plot_polygons(paindrawr_data = pdr_data, background_image = pdr_example_file("mird_body_background.png"))
  
```


## Merging by union

### ...we store this polygon as 'lb_poly'

```{r}
#| echo: true

lb_poly <- pdr_example_anatomy |>
  filter(str_detect(id, "(Mid_back_bottom)|(Back.+(lowerback|buttock))")) |>
  pdr_implode() |> 
  mutate(pdr_data = pdr_polygonize(pdr_data)) |>
  mutate(pdr_data = pdr_modify_polygons(pdr_data, "merge_overlaps")) |>
  mutate(lb_template = pdr_get_info(pdr_data, ".polygons"))
lb_poly |> pdr_plot_polygons(paindrawr_data = pdr_data, background_image = pdr_example_file("mird_body_background.png"))
  
```

## Bring it all together

### ..the raw pain drawwing

```{r}
pdr_example_data[1,] |> 
  pdr_plot_drawing(background_image = pdr_example_file("mird_body_background.png"))
```

## Bringing it all together

### ..the polygonized and merged pain drawing

```{r}
pdr1 <- pdr_example_data[1,] |>
  mutate(pdr_data = pdr_polygonize(pdr_data, buffer=10)) |> 
  mutate(pdr_data = pdr_modify_polygons(pdr_data, "merge_overlaps")) |>
  mutate(lb_template = lb_poly$lb_template) 
pdr1 |>  pdr_plot_polygons(pdr_data, background_image = pdr_example_file("mird_body_background.png"))

area_pdr1 <- pdr1 |>
  mutate(area = pdr_poly_areas(pdr_data)) |> pull(area)
```

..which has an area of `r round(area_pdr1)`

## Bring it all together

### ..reduced to 'low back' intersection

```{r}
pdr2 <- pdr_example_data[1,] |>
  mutate(pdr_data = pdr_polygonize(pdr_data, buffer=10)) |> 
  mutate(pdr_data = pdr_modify_polygons(pdr_data, "merge_overlaps")) |>
  mutate(lb_template = lb_poly$lb_template) |>
  mutate(pdr_data2 = pdr_modify_polygons(pdr_data, ops="reduce_by_template", template=lb_template)) 

pdr2 |> pdr_plot_polygons(pdr_data2, background_image = pdr_example_file("mird_body_background.png"))

area_pdr2 <- pdr2 |>
  mutate(area = pdr_poly_areas(pdr_data2)) |> pull(area)
```

..which has an area of `r round(area_pdr2)`

## All together now

```{r}
pdr_example_data |>
  mutate(pdr_data = pdr_polygonize(pdr_data, buffer=10)) |> 
  mutate(pdr_data = pdr_modify_polygons(pdr_data, "merge_overlaps")) |>
  mutate(lb_template = lb_poly$lb_template) |>
  mutate(pdr_data2 = pdr_modify_polygons(pdr_data, ops="reduce_by_template", template=lb_template)) |>
  mutate(total_area = pdr_poly_areas(pdr_data)) |>
  mutate(lbp_area = pdr_poly_areas(pdr_data2)) |> 
  dplyr::select(id, total_area, lbp_area)
```
